Adaptive broadcast tree for multicores

### 2013-06-07 graphs/visu_sbrinz_sequential.tex
New visualization applied to all combinations of machines and topologies except for rings

\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
\node at (0mm,0mm) {core 00};
\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
\node at (0mm,240mm) {Machine: sbrinz, topology: sequential};
\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (90mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (100mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (110mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (120mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (130mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (140mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (150mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (160mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (170mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (180mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (190mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (80mm,165mm) {};
\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (90mm,150mm) {};
\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (100mm,135mm) {};
\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (110mm,120mm) {};
\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (110mm,225mm) {};
\draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (120mm,210mm) {};
\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (130mm,195mm) {};
\draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (140mm,180mm) {};
\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (150mm,105mm) {};
\draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (160mm,90mm) {};
\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (170mm,75mm) {};
\draw[->,very thick,color=red] (s_0_5.center) -- (r_0_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (180mm,60mm) {};
\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (181mm,45mm) {};
\draw[->] (s_0_3.center) -- (r_0_3.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (191mm,30mm) {};
\draw[->] (s_0_2.center) -- (r_0_2.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (201mm,15mm) {};
\draw[->] (s_0_1.center) -- (r_0_1.center);

>>>>

\node (core_0_label) at (0mm,0mm) {core 00};
\node (core_1_label) at (0mm,5mm) {core 01};
\node (core_2_label) at (0mm,10mm) {core 02};
\node (core_3_label) at (0mm,15mm) {core 03};
\node (core_4_label) at (0mm,20mm) {core 04};
\node (core_5_label) at (0mm,25mm) {core 05};
\node (core_6_label) at (0mm,30mm) {core 06};
\node (core_7_label) at (0mm,35mm) {core 07};
\node (core_8_label) at (0mm,40mm) {core 08};
\node (core_9_label) at (0mm,45mm) {core 09};
\node (core_10_label) at (0mm,50mm) {core 10};
\node (core_11_label) at (0mm,55mm) {core 11};
\node (core_12_label) at (0mm,60mm) {core 12};
\node (core_13_label) at (0mm,65mm) {core 13};
\node (core_14_label) at (0mm,70mm) {core 14};
\node (core_15_label) at (0mm,75mm) {core 15};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_11) at (20mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_10) at (24mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_9) at (28mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_8) at (32mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_15) at (36mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_14) at (40mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_13) at (44mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_12) at (48mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_7) at (52mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_6) at (56mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_5) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (64mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (68mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (72mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (76mm,0mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_11) at (32mm,55mm) {};
\draw[->,semithick,color=red] ($(s_0_11.east)-(1mm,0mm)$) -- ($(r_0_11.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_10) at (36mm,50mm) {};
\draw[->,semithick,color=red] ($(s_0_10.east)-(1mm,0mm)$) -- ($(r_0_10.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_9) at (40mm,45mm) {};
\draw[->,semithick,color=red] ($(s_0_9.east)-(1mm,0mm)$) -- ($(r_0_9.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_15) at (44mm,75mm) {};
\draw[->,semithick,color=red] ($(s_0_15.east)-(1mm,0mm)$) -- ($(r_0_15.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_8) at (44mm,40mm) {};
\draw[->,semithick,color=red] ($(s_0_8.east)-(1mm,0mm)$) -- ($(r_0_8.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_14) at (48mm,70mm) {};
\draw[->,semithick,color=red] ($(s_0_14.east)-(1mm,0mm)$) -- ($(r_0_14.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_13) at (52mm,65mm) {};
\draw[->,semithick,color=red] ($(s_0_13.east)-(1mm,0mm)$) -- ($(r_0_13.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_12) at (56mm,60mm) {};
\draw[->,semithick,color=red] ($(s_0_12.east)-(1mm,0mm)$) -- ($(r_0_12.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_7) at (60mm,35mm) {};
\draw[->,semithick,color=red] ($(s_0_7.east)-(1mm,0mm)$) -- ($(r_0_7.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_6) at (64mm,30mm) {};
\draw[->,semithick,color=red] ($(s_0_6.east)-(1mm,0mm)$) -- ($(r_0_6.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_5) at (68mm,25mm) {};
\draw[->,semithick,color=red] ($(s_0_5.east)-(1mm,0mm)$) -- ($(r_0_5.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (72mm,20mm) {};
\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (72mm,15mm) {};
\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (76mm,10mm) {};
\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (80mm,5mm) {};
\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
\begin{pgfonlayer}{background}
\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1)] (allobjects) {};
\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1),scale=1.1] (bg) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (numa_axis_4.west),rounded corners] {};
\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (numa_axis_8.west),rounded corners] {};
\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west),rounded corners] {};
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: sbrinz, topology: sequential};
\end{pgfonlayer}
